### 2015-07-15 thesis/thesis/chap1/chap1.tex
behaivour

\section{Thesis Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in Chapter 2 the background needed for our research along with relevant related work. We introduce the web services and the concept of communities of web services and the theoretical background used throughout the these. Chapter 3 provides an efficient method of coalition formation for web services. In this chapter we have addressed $[R1]$, $[R2]$, $[R3]$ research questions on efficient ways of community formation.  Chapter 4 presents a distributed method of formation of web services communities. In this chapter we address $[R4]$, $[R5]$ research questions by proposing DDM, a distributed decision making mechanism for our web services which can perform in distributed manner and when information is incomplete. In Chapter 5 we delve into internal management of communities of web services and we address the $[R6]$ research question by analyzing the cooperative behaviour within the communities of web services. Finally in Chapter 6, we present our conclusion and future plan.

>>>>

\section{Thesis Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in Chapter 2 the background needed for our research along with relevant related work. We introduce the web services and the concept of communities of web services and the theoretical background used throughout the these. Chapter 3 provides an efficient method of coalition formation for web services. In this chapter we have addressed $[R1]$, $[R2]$, $[R3]$ research questions on efficient ways of community formation.  Chapter 4 presents a distributed method of formation of web services communities. In this chapter we address $[R4]$, $[R5]$ research questions by proposing DDM, a distributed decision making mechanism for our web services which can perform in distributed manner and when information is incomplete. In Chapter 5 we delve into internal management of communities of web services and we address the $[R6]$ research question by analyzing the cooperative behavior within the communities of web services. Finally in Chapter 6, we present our conclusion and future plan.

### 2015-07-15 thesis/thesis/chap4/chap4.tex
behaivour

In next chapter, we analyse the internal community behaviour of web services, and propose a model for competing and cooperating agents within the communities of web services.

>>>>

In next chapter, we analyse the internal community behavior of web services, and propose a model for competing and cooperating agents within the communities of web services.

### 2015-07-15 thesis/thesis/chap6/chap6.tex
behaivour

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behaviour of intelligent services that are active within communities. We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real services dataset on the web. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.

>>>>

In our final step of the work, the focus was on inter-community interaction between services involved within the community. The contribution of this model is the proposition of a coopetitive strategic model to analyze the interacting behavior of intelligent services that are active within communities. We considered two acting strategies where service agenets expect different sort of payoffs: (1) competitive strategy where the service claims that it can accomplish a task and therefore can take the responsibility over the service consumer satisfaction; and (2) cooperative strategy where the service does not take the responsibility to accomplish the task and only cooperates with competitive peers. Our proposed model advances the state-of-the-art in cooperative systems by enabling intelligent agent-based services to effectively choose their interacting strategies that lead to optimal outcomes. The proposed framework provides a reasoning technique that service agents can use to increase their overall obtained utilities. The theoretical results presented in this thesis are also backed by simulation results using a real services dataset. Moreover, we conduct extensive simulations, analyze various scenarios, and confirm the obtained theoretical results using parameters from a real services dataset on the web. Those results showed that our model outperforms existing competitive and random coopetitive strategies and the more
services deviate from the coopetitive strategy suggested by our decision-making mechanism the more they make less benefits.
